``Don't tell me what is, tell me what to do'':\\Instance-Based Planning for Actionable Analytics

### 2015-04-12 manuscript.tex
Updates from ShareLaTeX

  \author{\IEEEauthorblockN{Rahul Krishna, Tim Menzies, Xipeng Sheng}
    \IEEEauthorblockA{
      Computer Science, North Carolina State University, USA\\
  i.m.ralk, tim.menzies, xipengshen@gmail.com}\and
  \IEEEauthorblockN{Andrian Marcus}
   \IEEEauthorblockA{
      Computer Science, University of Texas, Dallas,  USA\\
  amarcus@utdallas.edu}}

@@

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
    \hline  2 & $\alpha=0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
    \hline  4 &     $\alpha=0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
    4 &   $\alpha=0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
    4 & $\alpha=0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
    \hline  5 &    $\alpha=0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
    5 &      $\alpha=0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
    \hline  6 &     $\alpha=0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
    6 &   $\alpha=0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
    \hline \end{tabular}\\}

@@

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
1 &   $\alpha=0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
1 & $\alpha=0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
\hline  2 & $\alpha=0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
\hline  3 &    $\alpha=0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
3 &  $\alpha=0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
\hline  4 & $\alpha=0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
\hline  5 & $\alpha=0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
5 &   $\alpha=0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
\hline  6 & $\alpha=0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
\hline \end{tabular}}\\

@@

    {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
        \arrayrulecolor{darkgray}
        \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
        1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
        \hline  2 & $\alpha=0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
        \hline  3 & $\alpha=0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
        \hline  4 & $\alpha=0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
        \hline  5 &     $\alpha=0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
        5 &   $\alpha=0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
        \hline  6 &    $\alpha=0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
        6 &      $\alpha=0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
        \hline  7 &   $\alpha=0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
        7 &     $\alpha=0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
        \hline \end{tabular}}\\

@@

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
      \hline  2 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
      \hline  3 & $\alpha=0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
      \hline  4 &   $\alpha=0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
      4 & $\alpha=0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
      \hline  5 & $\alpha=0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
      5 &  $\alpha=0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
      5 &    $\alpha=0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
      \hline  6 &   $\alpha=0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
      6 & $\alpha=0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
      \hline \end{tabular}}\\
\end{minipage}
\end{figure}
\begin{figure}
\begin{minipage}{0.5\textwidth}
  \renewcommand{\baselinestretch}{}
{\bf \scriptsize Log4j}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $\alpha=0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
      1 & $\alpha=0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
      1 & $\alpha=0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
      1 &  $\alpha=0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
      1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
      1 &   $\alpha=0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
      \hline  2 &    $\alpha=0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
      2 & $\alpha=0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
      2 & $\alpha=0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
      2 &   $\alpha=0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
      \hline \end{tabular}}\\

@@

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $\alpha=0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
    1 &  $\alpha=0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
    \hline  2 &   $\alpha=0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
    2 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
    2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
    2 & $\alpha=0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
    \hline  3 & $\alpha=0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
    \hline  4 & $\alpha=0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
    4 &  $\alpha=0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
    4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\

@@

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $\alpha=0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
    1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
    1 & $\alpha=0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
    \hline  2 &     $\alpha=0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
    2 &   $\alpha=0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
    \hline  3 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
    3 &    $\alpha=0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
    \hline  4 &     $\alpha=0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
    4 &      $\alpha=0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
    4 &   $\alpha=0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
    \hline \end{tabular}}  \\

@@

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $\alpha=0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
      1 & $\alpha=0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
      \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
      \hline  3 & $\alpha=0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
      3 & $\alpha=0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
      3 & $\alpha=0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
      \hline  4 & $\alpha=0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
      4 & $\alpha=0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
      4 & $\alpha=0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
      4 & $\alpha=0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
      \hline \end{tabular}}\\

@@

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $\alpha=0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
      1 & $\alpha=0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
      1 &   $\alpha=0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
      \hline  2 &    $\alpha=0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
      2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
      2 &  $\alpha=0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
      2 & $\alpha=0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
      2 & $\alpha=0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
      2 & $\alpha=0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
      2 &   $\alpha=0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
      \hline \end{tabular}}
 \end{minipage}  
   \end{figure}

>>>>

@@

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 &     Baseline &    0.03  &  0.0 & \quart{0}{0}{0}{62} \\
    \hline  2 & $0.25$, Prune=50\% &    0.15  &  0.09 & \quart{4}{6}{7}{62} \\
    \hline  3 & $0.5$, Prune=50\% &    0.25  &  0.1 & \quart{12}{6}{14}{62} \\
    \hline  4 &     $0.25$ &    0.34  &  0.05 & \quart{18}{4}{20}{62} \\
    4 &   $0.25$, weight &    0.36  &  0.08 & \quart{18}{5}{21}{62} \\
    4 & $0.75$, Prune=50\% &    0.41  &  0.13 & \quart{21}{8}{24}{62} \\
    \hline  5 &    $0.5$, weight &    0.46  &  0.18 & \quart{24}{12}{27}{62} \\
    5 &      $0.5$ &    0.53  &  0.15 & \quart{27}{10}{32}{62} \\
    \hline  6 &     $0.75$ &    0.64  &  0.17 & \quart{34}{11}{39}{62} \\
    6 &   $0.75$, weight &    0.73  &  0.17 & \quart{38}{11}{45}{62} \\
    \hline \end{tabular}\\}

@@

{\scriptsize \begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor[gray]{.9} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
1 &   Baseline &    0.16  &  0.03 & \quart{0}{3}{1}{111} \\
1 &   $0.25$ &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
1 & $0.25$, weight &    0.17  &  0.06 & \quart{0}{7}{2}{111} \\
\hline  2 & $0.25$, Prune=50\% &    0.22  &  0.06 & \quart{5}{8}{9}{111} \\
\hline  3 &    $0.5$ &    0.25  &  0.1 & \quart{3}{14}{13}{111} \\
3 &  $0.5$, weight &    0.26  &  0.14 & \quart{7}{19}{14}{111} \\
\hline  4 & $0.5$, Prune=50\% &    0.32  &  0.16 & \quart{10}{21}{22}{111} \\
\hline  5 & $0.75$, weight &    0.38  &  0.19 & \quart{14}{25}{30}{111} \\
5 &   $0.75$ &    0.4  &  0.12 & \quart{23}{16}{32}{111} \\
\hline  6 & $0.75$, Prune=50\% &    0.47  &  0.15 & \quart{30}{19}{42}{111} \\
\hline \end{tabular}}\\

@@

    {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
        \arrayrulecolor{darkgray}
        \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
        1 &     Baseline &    0.06  &  0.0 & \quart{0}{0}{0}{79} \\
        \hline  2 & $0.25$, Prune=50\% &    0.14  &  0.04 & \quart{4}{3}{6}{79} \\
        \hline  3 & $0.5$, Prune=50\% &    0.2  &  0.06 & \quart{9}{5}{11}{79} \\
        \hline  4 & $0.75$, Prune=50\% &    0.27  &  0.14 & \quart{10}{12}{17}{79} \\
        \hline  5 &     $0.25$ &    0.41  &  0.06 & \quart{27}{5}{29}{79} \\
        5 &   $0.25$, weight &    0.42  &  0.06 & \quart{27}{6}{30}{79} \\
        \hline  6 &    $0.5$, weight &    0.55  &  0.11 & \quart{35}{9}{41}{79} \\
        6 &      $0.5$ &    0.57  &  0.09 & \quart{37}{7}{43}{79} \\
        \hline  7 &   $0.75$, weight &    0.61  &  0.08 & \quart{42}{7}{46}{79} \\
        7 &     $0.75$ &    0.62  &  0.04 & \quart{46}{3}{47}{79} \\
        \hline \end{tabular}}\\

@@

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 &   Baseline &    0.05  &  0.0 & \quart{0}{0}{0}{75} \\
      \hline  2 & $0.25$, Prune=50\% &    0.11  &  0.05 & \quart{2}{4}{4}{75} \\
      \hline  3 & $0.5$, Prune=50\% &    0.16  &  0.1 & \quart{3}{8}{8}{75} \\
      \hline  4 &   $0.25$ &    0.2  &  0.08 & \quart{10}{6}{11}{75} \\
      4 & $0.25$, weight &    0.21  &  0.1 & \quart{7}{8}{12}{75} \\
      \hline  5 & $0.75$, Prune=50\% &    0.32  &  0.15 & \quart{15}{11}{21}{75} \\
      5 &  $0.5$, weight &    0.33  &  0.05 & \quart{19}{4}{22}{75} \\
      5 &    $0.5$ &    0.34  &  0.18 & \quart{18}{14}{23}{75} \\
      \hline  6 &   $0.75$ &    0.56  &  0.2 & \quart{27}{16}{40}{75} \\
      6 & $0.75$, weight &    0.56  &  0.26 & \quart{29}{20}{40}{75} \\
      \hline \end{tabular}}\\
\end{minipage}
\end{figure}
\begin{figure}
\begin{minipage}{0.5\textwidth}
  \renewcommand{\baselinestretch}{}
{\bf \scriptsize Log4j}

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $0.5$, Prune=50\% &    0.1  &  0.06 & \quart{1}{11}{5}{172} \\
      1 & $0.25$, Prune=50\% &    0.11  &  0.04 & \quart{1}{8}{7}{172} \\
      1 & $0.25$, weight &    0.1  &  0.03 & \quart{3}{6}{5}{172} \\
      1 &  $0.5$, weight &    0.1  &  0.13 & \quart{0}{24}{5}{172} \\
      1 &   Baseline &    0.11  &  0.04 & \quart{0}{7}{7}{172} \\
      1 &   $0.25$ &    0.12  &  0.06 & \quart{1}{11}{9}{172} \\
      \hline  2 &    $0.5$ &    0.15  &  0.09 & \quart{3}{17}{14}{172} \\
      2 & $0.75$, Prune=50\% &    0.15  &  0.05 & \quart{9}{9}{14}{172} \\
      2 & $0.75$, weight &    0.17  &  0.22 & \quart{9}{40}{18}{172} \\
      2 &   $0.75$ &    0.22  &  0.16 & \quart{14}{30}{27}{172} \\
      \hline \end{tabular}}\\

@@

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $0.25$, weight &    0.03  &  0.03 & \quart{0}{4}{1}{148} \\
    1 &  $0.25$ &    0.05  &  0.04 & \quart{1}{6}{4}{148} \\
    \hline  2 &   $0.5$ &    0.09  &  0.09 & \quart{6}{13}{10}{148} \\
    2 & $0.25$, Prune=50\% &    0.09  &  0.03 & \quart{7}{5}{10}{148} \\
    2 &  Baseline &    0.1  &  0.01 & \quart{10}{2}{12}{148} \\
    2 & $0.5$, weight &    0.14  &  0.06 & \quart{10}{9}{18}{148} \\
    \hline  3 & $0.5$, Prune=50\% &    0.19  &  0.08 & \quart{21}{12}{25}{148} \\
    \hline  4 & $0.75$, weight &    0.23  &  0.15 & \quart{22}{23}{31}{148} \\
    4 &  $0.75$ &    0.26  &  0.1 & \quart{27}{15}{36}{148} \\
    4 & $0.75$, Prune=50\% &    0.28  &  0.13 & \quart{30}{19}{39}{148} \\\hline \end{tabular}}\\

@@

{\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
    \arrayrulecolor{darkgray}
    \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
    1 & $0.25$, Prune=50\% &    0.09  &  0.15 & \quart{0}{9}{3}{62} \\
    1 &     Baseline &    0.09  &  0.05 & \quart{2}{3}{3}{62} \\
    1 & $0.5$, Prune=50\% &    0.12  &  0.13 & \quart{1}{8}{5}{62} \\
    \hline  2 &     $0.25$ &    0.24  &  0.3 & \quart{5}{19}{13}{62} \\
    2 &   $0.25$, weight &    0.25  &  0.32 & \quart{4}{20}{14}{62} \\
    \hline  3 & $0.75$, Prune=50\% &    0.37  &  0.45 & \quart{4}{29}{21}{62} \\
    3 &    $0.5$, weight &    0.49  &  0.5 & \quart{9}{32}{29}{62} \\
    \hline  4 &     $0.75$ &    0.53  &  0.47 & \quart{16}{30}{32}{62} \\
    4 &      $0.5$ &    0.53  &  0.28 & \quart{18}{18}{32}{62} \\
    4 &   $0.75$, weight &    0.61  &  0.43 & \quart{22}{27}{37}{62} \\
    \hline \end{tabular}}  \\

@@

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \arrayrulecolor{darkgray}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $0.25$ &    0.08  &  0.03 & \quart{0}{4}{1}{140} \\
      1 & $0.25$, weight &    0.09  &  0.05 & \quart{0}{7}{3}{140} \\
      \hline  2 & Baseline &    0.13  &  0.04 & \quart{6}{6}{9}{140} \\
      \hline  3 & $0.5$ &    0.16  &  0.09 & \quart{9}{13}{13}{140} \\
      3 & $0.25$, Prune=50\% &    0.17  &  0.04 & \quart{13}{6}{15}{140} \\
      3 & $0.5$, weight &    0.19  &  0.09 & \quart{12}{13}{18}{140} \\
      \hline  4 & $0.5$, Prune=50\% &    0.22  &  0.11 & \quart{15}{16}{22}{140} \\
      4 & $0.75$, weight &    0.25  &  0.1 & \quart{19}{15}{27}{140} \\
      4 & $0.75$ &    0.28  &  0.2 & \quart{19}{30}{31}{140} \\
      4 & $0.75$, Prune=50\% &    0.28  &  0.09 & \quart{24}{13}{31}{140} \\
      \hline \end{tabular}}\\

@@

  {\scriptsize\begin{tabular}{l@{~~~}l@{~~~}r@{~~~}r@{~~~}c}
      \rowcolor{Gray} \textbf{Rank} & \textbf{Treatment} & \textbf{Med} & \textbf{IQR} & \\
      1 & $0.75$, weight &    0.31  &  0.14 & \quart{0}{31}{13}{170} \\
      1 & $0.25$, weight &    0.32  &  0.1 & \quart{2}{22}{15}{170} \\
      1 &   $0.25$ &    0.32  &  0.06 & \quart{13}{14}{15}{170} \\
      \hline  2 &    $0.5$ &    0.34  &  0.11 & \quart{6}{25}{20}{170} \\
      2 &   Baseline &    0.36  &  0.13 & \quart{4}{30}{24}{170} \\
      2 &  $0.5$, weight &    0.35  &  0.12 & \quart{6}{28}{22}{170} \\
      2 & $0.5$, Prune=50\% &    0.36  &  0.12 & \quart{11}{27}{24}{170} \\
      2 & $0.25$, Prune=50\% &    0.38  &  0.1 & \quart{13}{23}{29}{170} \\
      2 & $0.75$, Prune=50\% &    0.37  &  0.21 & \quart{2}{47}{27}{170} \\
      2 &   $0.75$ &    0.38  &  0.17 & \quart{6}{39}{29}{170} \\
      \hline \end{tabular}}
 \end{minipage}  
   \end{figure}
